---
title: 'Population projections and harvest specifications for canary rockfish (\textit{Sebastes pinniger}) based on recent catches, updating projections from the 2023 stock assessment' 
author:  
  - name: 'Chantel Wetzel'  
    affiliations:  
      - name: 'NOAA Fisheries Northwest Fisheries Science Center'  
        address: '2725 Montlake Boulevard East'  
        city: 'Seattle, WA'  
        state: 'WA'  
        postal-code: '98112-2097'  
date: today  
keep-tex: true   
mainfont: 'Latin Modern Sans'   
pdf-engine: lualatex  
format:   
  pdf:   
    documentclass: article  
    papersize: letter  
    number-sections: false  
    template-partials:  
      - 'support_files/before-body.tex'  
      - 'support_files/_titlepage.tex'  
    include-in-header:  
      - 'support_files/in-header.tex'  
    toc: false  
    sansfont: 'Latin Modern Sans'  
    lof: false  
    lot: false  
    titlepage-geometry:   
      - top=2in  
      - bottom=1in  
      - right=1in  
      - left=1in  
output-file: 'catch_only_projection'
params:
  model_dir: "C:/Assessments/2026/cop_template/models"
  species: "canary rockfish"
  category: 1
  sigma: 0.50
  p_star: 0.45
  spawn_output_units: "(millions of eggs)"
---

```{r}
#| label: load-package
#| echo: false
#| warning: false
#| message: false

devtools::load_all("C:/Users/chantel.wetzel/Documents/github/catchonlyproj")

```


```{r}
#| label: model
#| echo: false
#| warning: false
#| message: false

base_model <- r4ss::SS_output(
  dir = file.path(params$model_dir, "stock_assessment_model"),
  verbose = FALSE,
  printstats = FALSE, 
  hidewarn = TRUE) 

cop_model <- r4ss::SS_output(
  dir = file.path(params$model_dir, "cop_model"),
  verbose = FALSE,
  printstats = FALSE, 
  hidewarn = TRUE) 
```


```{r}
#| label: get-model-values
#| echo: false
#| eval: true
#| warning: false
#| message: false

projection_table_base_model <- get_model_values(
  replist = base_model
)

projection_table_cop <- get_model_values(
  replist = cop_model
)

```


```{r}
#| label: tbl-combine
#| echo: false
#| eval: true
#| warning: false
#| message: false

combined_table <- combine_tables(
  base_model_table = projection_table_base_model,
  cop_model_table = projection_table_cop,
  assess_year = 2023
)

```


```{r}
#| label: text-parameters
#| echo: false
#| warning: false
#| message: false

# The year of benchmark or update model year that is being used in the COP
assess_year <- base_model$endyr + 1
# Current year for the text and grabbing values from the model object
current_year <- as.numeric(format(Sys.Date(), "%Y"))
# Spawning output/biomass used in the text
spawn_text <- tolower(base_model$SpawnOutputLabel)

```


:::{.landscape}

This document details a catch-only projection for `r params$species`. The most recent assessment for `r params$species` was conducted in `r assess_year`. This analysis updates catches between `r assess_year` - `r current_year` to the removals by year from the Groundfish Multiyear Mortality (GEMM) report. The removals for `r current_year` and `r current_year + 1` were set equal to mortality projections provided by the Groundfish Management Team (GMT). For years `r current_year + 2` and beyond, removals were set equal to the projected Acceptable Biological Catch (ABC) based on a category `r params$category` time-varying $\sigma$ of `r params$sigma` and a P* value of `r params$p_star`.

\vspace{0.25in}

```{r}
#| label: caption
#| echo: false
#| eval: true
#| warning: false
#| message: false

table_caption <- glue::glue("Original {assess_year} projection and new catch-only projection for OFLs (mt), buffer, ABCs (mt), actual & assumed catch (mt), ACLs (mt), {spawn_text} {params$spawn_output_units}, and stock status (fraction of unfished {spawn_text}) given the removals. The gray shading indicates values associated with the original {assess_year} assessment projection. In both the original model and the new projection, the removals for years beyond the values in the 'Actual & Assumed Removals' columns are the ACL values estimated from that model.")

```


```{r}
#| label: tbl-proj
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| tbl-cap: !expr table_caption

format_table(
  table = combined_table,
  assess_year = 2023,
  sb_decimal_number = 0,
  hl_decimal_number = 0
)


```



